Tree size, exposure, and hydraulic traits interactively shape drought response in a temperate broadleaf forest

### 2019-06-29 manuscript/03-methods.Rmd
Update 03-methods.Rmd
remove issue #35

`diam_1999 = dbh2008 - 2*(bark.depth2008) - 2*(sum(ring.width1999:ring.width2008)) + 2*(bark.depth_1999)`  ([issue #35](https://github.com/SCBI-ForestGEO/McGregor_climate-sensitivity-variation/issues/35)) (**clean up this equation--put a generic year instead of 1999, use sum symbol, etc.**)

>>>>

`diam_1999 = dbh2008 - 2*(bark.depth2008) - 2*(sum(ring.width1999:ring.width2008)) + 2*(bark.depth_1999)`  (**clean up this equation--put a generic year instead of 1999, use sum symbol, etc.**)
